---
title: "Turkey Meatball and Saffron Orzo"
format: html
editor: visual
---

## Ingredients

### Prep

```{r, include=FALSE, echo=FALSE}

Spices = c("Garlic powder",
"Red Chili flakes", 
"Salt",
"Pepper", 
"Saffron",
"Parsley",
"Oregano")

Pantry = c(
"Breadcrumbs",
"Orzo",
"",
"",
"",
"",
"")

Fridge = c(
"Parm",
"Butter",
"Turkey",
"Lemon",
"1 Egg",
"Better than Bouillon Chicken Paste (if using)",
"")

prep_df = data.frame(Fridge, Pantry, Spices)
```

```{r, echo=FALSE}

knitr::kable(prep_df)
```

### Meatballs

-   1 lb ground turkey
-   40g parmesean cheese (fresh grated)
-   3 tbsp dried parsley
-   2 tsp lemon zest
-   1 egg
-   1/2 cup breadcrumbs
-   Some chicken stock or water + bouillon powder (enough to cover the bottom of the pan)
-   Salt and pepper
-   1 tsp garlic powder
-   1/2 tsp red pepper flakes

### Orzo

-   80g butter
-   1 onion or shallot, diced
-   2 garlic gloves, diced
-   "Pinch" of Saffron (I use a container in Germany that has .2 grams)
-   200g orzo
-   20g parmesean cheese
-   1/2 tsp red pepper flakes
-   475ml chicken stock
-   2 tbsp oregano

1.  **Make meatballs**: Put ground turkey, lemon zest, parm, egg, breadcrumbs in a bowl, add salt and pepper, garlic powder and red pepper, then mix well and form meatballs (between 12-20)

2.  **Cook the base for the Orzo**: Melt half the butter (40g) with a splash of oil on medium heat, then add onions. Cook for 2 minutes or so, until softened, then add garlic and 1/2 tsp pepper flakes and cook for two more minutes.

3.  **Start Orzo cook**: Add the orzo, saffron and stock and bring to a boil. Reduce heat to med-low and cover. Cook for around 10 minutes (stirring is allowed: keep an eye on it, if it seems too dry or to be sticking lift the lid a stir).

4.  **Make meatballs**: Heat a pan over medium high heat and then add some oil, and add the meat balls. Let them get some color (well browned) and flip them carefully (using a fork or tongs). Pour in the stock and bring down to a simmer and allow for cooking (at least 5 more minutes)

5.  **Finish orzo**: When orzo is done, give it a stir, add the remaining cheese, butter and oregano. Season to taste.
